---
title: "GO Analysis on mus-musculus dataset"
output: html_document
---

```{r setup, include=FALSE}

library(clusterProfiler)
library(magrittr)
library(dplyr)
library(clusterProfiler)
library(ggplot2)
library(tidyr)
library(tidytext)
library(SummarizedExperiment)
library(org.Mm.eg.db)

knitr::opts_chunk$set(echo = FALSE)

```

## R Markdown

```{r}
# ----- Dataset -------------
data_file <- readRDS("../data/data14Features.rds")

analysis_data <- data_file@metadata$limma[, "Sirt_vs_Mock", ] %>%
  as.data.frame() %>%
  dplyr::select(effect,p) %>%
  cbind(.,ENTREZ_ID = rowData(data_file)$ENTREZID)

analysis_data$ENTREZ_ID <- analysis_data$ENTREZ_ID %>%
  stringr::str_split(.,";",simplify=TRUE) %>%
  .[,1]

geneList <- analysis_data %>% dplyr::filter(ENTREZ_ID != "" & effect != "") %>%   dplyr::select(ENTREZ_ID,effect,p)

#define groups 1-3
geneList <- mutate(geneList, grp_id = ifelse(p <= 0.05 & effect <= 0, 1,
                                                   ifelse(p <= 0.05 & effect >= 0, 2, 3)))



# Remove duplicate values
any(duplicated(geneList$ENTREZ_ID))
# --- Filter for non duplicated items - Not implemented


```


```{r}
# Option 1 - 
no_of_grps <- geneList$grp_id %>% unique() %>% .[!is.na(.)]

ora_list <- no_of_grps %>% lapply(., function(x){
  gene_oi <- geneList %>% dplyr::filter(grp_id == x & ENTREZ_ID != "")
  enrichr_result <- enrichGO(gene = gene_oi$ENTREZ_ID,
                             universe = geneList$ENTREZ_ID,
                             OrgDb = org.Mm.eg.db,
                             ont = "CC",
                             pvalueCutoff = 0.01,
                             pAdjustMethod = "BH",
                             qvalueCutoff = 0.05,
                             readable = TRUE)
  enrichr_result@result %>%
    dplyr::mutate(p_log = -1*log(pvalue, 10))%>%
    dplyr::filter(p_log > 1.3) -> enrchresult_Grp
  enrchresult_Grp %>% 
    mutate(grp_id = x)
})

# Bind data frames returned from all groups  and save it as a data frame
# do.call(rbind, .) only accepts lists. hence we convert it into a DF in the next line
ora_list_df <- ora_list %>% do.call(rbind, .)
```


```{r}
# Option 2 - a seperate gene data frame is used
gene <- geneList$ENTREZ_ID

gene.df <- bitr(gene, 
                fromType = "ENTREZID",
                toType = c("ENSEMBL","SYMBOL"),
                OrgDb = org.Mm.eg.db)
head(gene.df)

e_go_2 <- enrichGO(gene = gene.df$ENSEMBL,
                   universe = geneList,
                   OrgDb = org.Mm.eg.db,
                   keyType = "ENSEMBL",
                   ont = "CC" ,
                   pvalueCutoff = 0.01,
                   pAdjustMethod = "BH",
                   qvalueCutoff = 0.05)
head(e_go_2)

# Map Gene ID to Gene Symbol using setreadable() or readble = TRUE
e_go_2_symbol <- setReadable(e_go_2, OrgDb = org.Mm.eg.db)
head(e_go_2_symbol)


